Scalable and Parameter-Free Exploration in Deep Reinforcement Learning

### 2022-01-12 papers/main.tex
TEMPORARY DEPLOY COMMIT

Functional variational Bayesian neural networks \citep{sun_functional_2019} is 
a variational inference method for neural networks that approximates the 
posterior distribution in function space. This means that our prior will be a distribution
over functions, also known as a stochastic process.
\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):

@@

where \(\X \in \mathcal{X}^n\) is a finite measurement set and \(P_\X, Q_\X\) are the marginal distributions
at \(\X\). They further show that if \(\f^\X\) are the function values at points \(\X\), then

\begin{multline}\label{eq:fkl}
    \nabla_\phi \KL[q_\phi(\f^X) \Vert p(\f^\X)] \\
    = \E \left[ \nabla_\phi \f^\X( \nabla_\f \log q(\f^\X) - \nabla_\f \log p(\f^\X)) \right].
\end{multline}

@@

\section{Method}
% Motivation:
% * Optimal regret
% * Meaningful priors
We will present a method that allows the following:

\begin{itemize}
    \item Optimal regret
    \item Incorporate domain knowledge
    \item Avoid hyperparameter optimization
\end{itemize}

@@

We would like to approximate the posterior distribution of the Q-value function.
This would (1) give optimal regret, (2) let us incorporate domain knowledge
through an appropriate prior distribution.
We can use the functional variational bayesian neural
network (FVBNN)~\citep{sun_functional_2019} framework discussed earlier.
NoisyNet uses one sample from Q for each optimization step. We will instead use
\(N\) samples
from Q. This lets us add the KL-term from FVBNN to the loss function that
encourages stochasticity.
The maximization target becomes:
\begin{equation}
    \log p(\D_\omega^N \vert f) - \KL \left[ q(\f^{\D_\omega^N}, \f^M) \Vert p(\f^{\D_\omega^N}, \f^M) \right],
\end{equation}
where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^M\) is \(f\) applied to
a set of i.i.d. random points \(M = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
with full support. We will let

>>>>

Functional variational Bayesian neural networks \citep{sun_functional_2019} is 
a variational inference method for neural networks that approximates the 
posterior distribution in function space. This means that our prior will be a distribution
over functions, also known as a stochastic process.
\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\), the
KL-divergence from \(Q\) to \(P\) is the supremum of the marginal KL-divergences over
all finite measurement sets. Let \(P_\X\) be the marginal distribution of function values
at \(\X \in \mathcal{X}^n\), then:

@@

Now the stochastic processes are a neural network \(q_\phi\) and a prior \(p\). In a similar
manner to NoisyNet, we sample a function \(f\) from \(q\) by sampling a random noise vector
\(\xi\), and then defining \(f(\bm{x}) = g_\phi(\bm{x}, \xi)\). They further show that the
gradient of the KL-divergence for functions evaluated at the measurement set \(\X\) is

\begin{multline}\label{eq:fkl}
    \nabla_\phi \KL[q_\phi(\f^\X) \Vert p(\f^\X)] = \E_q \left[ \nabla_\phi \log q_\phi (\f^\X) \right]\\
    + \E_\xi \left[ \nabla_\phi \f^\X( \nabla_\f \log q(\f^\X) - \nabla_\f \log p(\f^\X)) \right].
\end{multline}

The measurement set \(\X\) is created by concatenating the training points \(\X^D\) and a
set of \(M\) points \(\X^M\) drawn from some distribution \(c\) that has full support
in the space of interesting test cases.

@@

\section{Method}
% Motivation:
% * Optimal regret
% * Meaningful priors
We will present a method based on functional variational Bayesian neural
networks~\citep{sun_functional_2019} that allows the following:

\begin{itemize}
    \item Near-optimal regret
    \item Incorporate domain knowledge
    \item Avoid hyperparameter optimization
\end{itemize}

@@

We would like to approximate the posterior distribution of the Q-value function.
This would (1) give near-optimal regret, (2) let us incorporate domain knowledge
through an appropriate prior distribution.
We can use the functional variational bayesian neural
network (FVBNN)~\citep{sun_functional_2019} framework discussed earlier.
NoisyNet uses one sample from Q for each optimization step. We will instead use
\(N\) samples
from Q. This lets us add the KL-term from FVBNN to the loss function that
encourages stochasticity.
The maximization target becomes:
\begin{equation}
    \log p(\D_\omega^N \vert f) - \KL \left[ q(\f^{\D_\omega^N}, \f^M) \Vert p(\f^{\D_\omega^N}, \f^M) \right],
\end{equation}
where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^M\) is \(f\) applied to
a set of i.i.d. random points \(M = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
with full support. We will let
